\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{vwcol}
\usepackage{tikz}

\usepackage{paracol}

% Remove page numbers
\pagestyle{empty}

\setlength{\parindent}{0pt}

% Define section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% Define subsection formatting for job titles
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing{\subsection}{0pt}{8pt}{2pt}

% Remove default list formatting
\setlist[itemize]{leftmargin=0pt, itemsep=2pt, parsep=0pt, topsep=4pt}

\newcommand{\street}{5710 N Winthrop Ave}
\newcommand{\city}{Chicago}
\newcommand{\state}{IL}
\newcommand{\zip}{60660}
\newcommand{\phone}{(219) 208-0068}
\newcommand{\email}{csreid.cr@gmail.com}

\newcommand{\makeaddress}{%
	\street \\
	\city, \state \zip \\
	\phone \\
	\email
}

\newcommand{\job}[4]{%
	\subsection{#1 --- #2}
	\textit{#3}

	#4

	\vspace{0.1in}
}

\begin{document}

% Name header
\begin{flushright}
{\huge\bfseries{Cameron Reid}}\\
\makeaddress
\end{flushright}

\columnratio{0.6}
\setlength\columnsep{30pt}
\begin{paracol}{2}

\section{Experience}

	\job{Jacobian Labs}{Founder/Principal Engineer}{June 2023 - Present}{Founded consulting practice focused on building reliable, robust software systems for clients across diverse industries, specializing in machine learning and scalable architecture.}

	\job{Klaviyo}{Senior Software Engineer}{June 2022 - June 2023}{Klaviyo ingests a huge amount of data from various e-commerce integrations. My team and I were responsible for reliably and efficiently managing that huge stream of incoming data.}

	\job{Sense}{Senior Software Engineer}{February 2021 - June 2022}{Working on the chatbot team, I helped guide the development of Sense's primary AI product to provide a conversational AI assistant using deep learning NLU techniques.}

	\job{Kerauno}{Principal Software Engineer}{September 2018 - November 2019}{I helped guide a team of engineers to build the backbone of Kerauno's next-generation communications workflow platform using modern best practices, including robust relational data modeling in PostgreSQL and Golang microservices orchestrated with Kubernetes.}

	\job{Torchlite}{Senior Platform Engineer}{December 2015 - September 2018}{I served as a founding member of the engineering team at a very small startup, handling all of the back-end architecture and implementation.}

	\job{Emerging Threats / Proofpoint}{Software Engineer}{July 2014 - December 2015}{I joined Emerging Threats, an Indianapolis cybersecurity startup, and immediately became interested in the problems of robustly managing big data.}

\switchcolumn

\section{Tools}

	Expert with \textbf{Docker, Kubernetes}, and other containerization technologies

	\vspace{0.1in}

	Expert level knowledge of \textbf{PostgreSQL} specifically and relational database systems generally.

	\vspace{0.1in}

	Experience using \textbf{PyTorch, TensorFlow, Keras}, and other machine learning frameworks.

	\vspace{0.1in}

	Technical polyglot with professional expertise in many languages including Python, Java(/Type)Script, Scala, Rust, Ruby, Go and more

	\vspace{0.1in}
	Extensive experience with \textbf{AWS, Azure, and GCP} cloud computing platforms.

\vspace{0.2in}

\section{Notable Work}

\textbf{Chatbot V2} is a successor to the Sense chatbot that is more scalable, more maintainable, and more stable than its predecessor, allowing Sense to feel confident selling AI in a demanding market.

\vspace{0.1in}

\textbf{Mutual Reinforcement Learning} is the result of research into novel multi-agent machine learning algorithms

\vspace{0.1in}

\textbf{Kerauno Event Engine:} The high-throughput, fault-tolerant, distributed event reactor at the heart of the Kerauno communication orchestration platform.

\vspace{0.2in}

\section{Education}

\textbf{University of Illinois, Chicago} \\
Ph.D.: 2024-present

\vspace{0.1in}

\textbf{Purdue University, Indianapolis} \\
M.Sc. May 2021

\vspace{0.1in}

\textbf{Purdue University, West Lafayette} \\
	BS May 2014

\end{paracol}

\end{document}
